Validating FF-Replan vs.\@ a State-Of-The-Art Probabilistic Planner in Translated Real World Domains

### 2014-03-30 FinalPaper/paper.tex
problem def

\section{Problem Formulation}

\subsection{Markov Decision Process}

\subsubsection{Goal-oriented MDPs}

\subsubsection{MDP with Finite Horizon}

\subsection{Planners}

@@

% depends if we should include this, what we tell about Gourmand / RDDL...

@@

In this paper we use Gourmand as a representative probabilistic planner, as
it's the improved version of Glutton, the runner-up of the IPPC-11 competition.

@@

\subsection{Planning problem}
\begin{itemize}
	\item Describe the MDP finite horizon planning problem (useful for modelling nearly infinite processes)
	\item reason about the \emph{augmented state space} of M(H), which is a set \emph{S x (0, ... , H)} of state number of steps-to-go pairs
	\item Describe reward heuristic
	\item Solving M(H) means finding a policy: a rule for selecting actions in augmented states so that executing the actions recommended by the policy starting in the initial state will accumulate the largest expected reward over H steps time
	\item The challenge or large branching factors (induced by natural dynamic)
\end{itemize}

@@

Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed. Problems that fail this test were deemed to be classical planning problems in disguise, favouring using replanners\cite{little2007probvsreplan}. This section describes interesting domains in which either FF-Replan or Gourmand prevailed during the International Probabilistic Planning Compeitions. We will then translate the most interesting domains to a complete "real-world" domain and evaluate them using the probabilistically interesting baseline test. This paper concludes on evaluation both planners using the translated domains.

@@

\section{Domain Descriptions}
Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed. Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}. This section describes interesting domains in which either FF-Replan or Gourmand prevailed during the International Probabilistic Planning Compeitions. These domains are evaluated for how well they portray real-world scenarios. The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario. Little et all's baseline test helps us to predict which planner would perform well on these domains. We will then conclude our evaluation by comparing these results to the result of our experiments described in Section \ref{sec:experiment}.

>>>>

\section{Background}

\subsubsection{Goal-oriented MDPs. }The problems in IPPC-04 were specified using the Planning Domain Description Language (PPDLL). PPDDL specifies a probabistic planning problem as a set of probabilistic action sets and an initial and goal state description in which every action has a certain probability assigned to it \cite{FFReplan}. The planners from IPPC-04 were evaluated on how many trials reached the goal per problem and the average number of actions selected when succesfull. These planning problems were however relatively easy to solve as they did not account for \emph{natural dynamics} and/or large branching factors that occur in more realtistic systems \cite{kolobov2012glutton}. FF-Replan \cite{FFReplan}, as specified in Section  kindly remembered the committee of the IPPC-04 that the specified planning problems that contained no dead-ends were fairly easy to solve using relatively simple tools to handle with uncertainty.

\subsubsection{MDP with Finite Horizon. }IPPC

@@

% depends if we should include this, what we tell about GOURMAND / RDDL...

@@

In this paper we use GOURMAND as a representative probabilistic planner, as
it's the improved version of Glutton, the runner-up of the IPPC-11 competition.

@@

\subsection{Planning problem}

\begin{itemize}
	\item Describe the MDP finite horizon planning problem (useful for modelling nearly infinite processes)
	\item reason about the \emph{augmented state space} of M(H), which is a set \emph{S x (0, ... , H)} of state number of steps-to-go pairs
	\item Describe reward heuristic
	\item Solving M(H) means finding a policy: a rule for selecting actions in augmented states so that executing the actions recommended by the policy starting in the initial state will accumulate the largest expected reward over H steps time
	\item The challenge or large branching factors (induced by natural dynamic)
\end{itemize}

@@

Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed. Problems that fail this test were deemed to be classical planning problems in disguise, favouring using replanners\cite{little2007probvsreplan}. This section describes interesting domains in which either FF-Replan or GOURMAND prevailed during the International Probabilistic Planning Compeitions. We will then translate the most interesting domains to a complete "real-world" domain and evaluate them using the probabilistically interesting baseline test. This paper concludes on evaluation both planners using the translated domains.

@@

\section{Domain Descriptions}
Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed. Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}. This section describes interesting domains in which either FF-Replan or GOURMAND prevailed during the International Probabilistic Planning Compeitions. These domains are evaluated for how well they portray real-world scenarios. The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario. Little et all's baseline test helps us to predict which planner would perform well on these domains. We will then conclude our evaluation by comparing these results to the result of our experiments described in Section \ref{sec:experiment}.
